18.821 Project 2

### 2014-10-28 paper/paper.tex
changed flipping definition

\subsection{Flipping}
Another notion that we will use in this paper is the concept of flipping. We define the \emph{flip} of a sequence $a$ as the sequence $b$ with the same elements as $a$, but with elements in the opposite order. More concretely, if $a = a_1, a_2, \dots, a_n$ for some arbitrary $n$, then the flip of the sequence $a$ will be the sequence $b = a_n, a_{n-1}, \dots, a_2, a_1$.

We will talk about how the flip of a sequence is important to this avoidance problem later in the paper.

>>>>

\subsection{Flipping}
Another notion that we will use in this paper is the concept of `flipping'. We define the \emph{flip} of a sequence $a$ as the sequence $b$ with the same elements as $a$, but with the largest element swapped with the smallest element, the second largest element swapped with the second smallest element, etc. For example, the flip of 1324 is 4321. We will discuss the flip as it becomes useful.
